Compiling refinement types to dependent types

### 2020-07-10 tex/paper.tex
Don't forget to add references to case splitting
Add stub syntax for case analysis

\begin{figure}[ht]
  \footnotesize
  \drules[TWF]{$\nonterm G \vdash \nonterm{ts} \text{ ok}$}{type well-formedness}{TrueRef,Base,Conj,Arr}
  \drules[T]{$\nonterm G \vdash \nonterm{es} : \nonterm{ts}$}{term typing}{BoolTop,BoolBot,Var,Abs,App,If,Sub}
  \caption{Surface language typing}
  \label{fig:surface_typing}
\end{figure}

@@

We take $\lambda C$ \cite{Nederpelt14} enriched with case-splitting as our core dependently typed language.

>>>>

\begin{figure}[ht]
  \footnotesize
  \drules[TWF]{$\nonterm G \vdash \nonterm{ts} \text{ ok}$}{type well-formedness}{TrueRef,Base,Conj,Arr}
  \drules[T]{$\nonterm G \vdash \nonterm{es} : \nonterm{ts}$}{term typing}{Unit,Var,Abs,App,Case,Sub}
  \caption{Surface language typing}
  \label{fig:surface_typing}
\end{figure}

@@

We take $\lambda C$ \cite{Nederpelt14} enriched with case-splitting inspired by \cite{TAPLVariants,EisenbergThesis} as our core dependently typed language.
